---
title: "InClassScript3"
author: "Qingqing Yang"
date: "03/02/2022"
output: word_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

## Question 1
Create data frame Q1_df
```{r}
Q1_df <- data.frame(
  categories=c("Orange","Blue","Green","Red","Maroon"),
  freq = c(21,21,18,19,20)
)
```

Plot the data
```{r}
barplot(Q1_df$freq,
        names.arg = Q1_df$categories, 
        ylim=c(0,25),
        space=0.1
)
```

## Question 2
Create data frame Q2_df
```{r}
library(knitr)
Q2_df <- data.frame(
  Participant = 1:15,
  Introspection = c(51,65,74,74,75,76,87,86,51,85,52,92,97,70,86),
  Optimism = c(55,80,71,66,74,68,51,67,74,67,81,83,87,74,84)
)
kable(Q2_df)
```
   

Calculate Pearson's r

```{r}
cor(Q2_df$Introspection, Q2_df$Optimism,method = "pearson")
```
The pearson's r equals 0.168.

------------------------------------

Plot the data and trend line
```{r}
plot(Q2_df$Introspection, Q2_df$Optimism,
     main = "Introspection and Optimism",
     xlab = "Introspection",
     ylab = "Optimism"
)

lm_Q2=lm(Q2_df$Introspection ~ Q2_df$Optimism)
abline(lm_Q2)
lm_Q2
```

Therefore, the equation should be:
$Optimism = 0.2423*Introspection+57.2557$  

      
## Question 3
Get the data frame for Q3
```{r}
Q3_df <- data.frame(
  Participant = 1:12,
  Visual_Imagery_Rating= c(44,38,40,43,47,31,42,42,48,28,40,41),
  Vivid_Dreaming = NaN
)
kable(Q3_df)
```
Temporary set the vivid dreaming value to be NaN


Calculate the y by $y=bx+a$
```{r}
slope = 0.004
intercept= 6.023
for (i in 1:12){
Q3_df$Vivid_Dreaming[i]=
  slope*Q3_df$Visual_Imagery_Rating[i]+intercept
}
kable(Q3_df)
```


## Question 4
Data frame Q4_df
```{r}
Q4_df <- data.frame(
  x = c(16,12,15,13,11),
  y_predicted= c(56.86,146.38,79.2415,124,168.76),
  residuals= c(-21.86,-66.38,30.76,26,31.24),
  y = NaN
)
kable(Q4_df)
```

Find y by $y_i=\hat{y}_i+residual_i$
```{r}
for (i in 1:5){
  Q4_df$y[i]=Q4_df$y_predicted[i]+Q4_df$residuals[i]
}
kable(Q4_df)
```

Plot x and y with range on x and y
```{r}
plot(Q4_df$x, Q4_df$y,
     main = "x and y",
     xlab = "x",
     ylab = "y",
    xlim = c(0,25),
    ylim = c(0,250),
)

# The h= and v= forms draw horizontal and vertical lines at the specified coordinates
abline(v=12)
```
  